### 2017-04-30 abstract.tex
IEEE format

Measuring the distance between two program executions is a fundamental problem in dynamic analysis of software, and useful in many test generation and debugging algorithms.  This paper proposes a novel metric for measuring distance between executions, and specializes it to the most common application, determining similarity of failing test cases.  The metric is based on a causal concept of distance: executions are similar to the degree that changes in the program itself, introduced using mutation operators, cause similar changes in the correctness of the executions.  Specifically, if two failing test cases (for the original program) become successful due to the same mutant, they are more likely to be due to the same fault.  We evaluate our metric using more than 50 faults and 2,800 test cases for two widely-used real-world compilers, and demonstrate improvements over state-of-the-art methods for fault identification and localization.

>>>>

Measuring the distance between two program executions is a fundamental problem in dynamic analysis of software, and useful in many test generation and debugging algorithms.  This paper proposes a metric for measuring distance between executions, and specializes it to an important application, determining similarity of failing test cases, for the purpose of automated fault identification and localization in debugging based on automatically generated compiler tests.  The metric is based on a causal concept of distance: executions are similar to the degree that changes in the program itself, introduced using mutation operators, cause similar changes in the correctness of the executions.  Specifically, if two failing test cases (for the original compiler) become successful due to the same mutant, they are more likely to be due to the same fault.  We evaluate our metric using more than 50 faults and 2,800 test cases for two widely-used real-world compilers, and demonstrate improvements over state-of-the-art methods for fault identification and localization.

### 2017-04-30 experiments.tex
small fixes
IEEE format

Table \ref{jstable} shows a comparison of three fault localization methods for the SpiderMonkey faults.  The first column shows, for each fault, identified by the commit number of the code change that first ``fixed'' the failing tests associated with the fault, its FPF ranking: this is \emph{not} a fault localization ranking, just a way to see that the localization success seems to be somewhat independent of the ease of distinguishing the failures for a fault.  The next four columns show localization rankings.  A dash for a column means that localization did not rank any faulty statements, or assigned all faulty statements suspiciousness of 0.0.  The four rankings are: the {\bf Coverage} localization, the {\bf Repair} localization, the MUSE \cite{MUSE} localization, and the MUSEUM \cite{multilingual} localization, which uses the same formula as MUSE, but works better for multiple faults because it uses only one failure.  The MUSE/MUSEUM formulas normally make use of information from passing tests as well: when mutating a statement makes a passing test case fail, it makes the statement \emph{less} suspicious, by a weighted amount. The weight assigned to information from passing tests in our setting would likely be low (due to the ratios of repairs to mutation kills).  In a limited sense, information from passing tests is already incorporated in our results.  Throwing out all mutants that are killed by any passing test as potential repairs/localizations ensures that the rankings of all statements that are in MUSE/MUSEUM rankings are correct, relative to each other.  By definition, passing tests have no influence on the suspiciousness of these mutants.  However, there may be other mutants that 1) repair a failure and 2) are killed by some test case: these could, if enough repaired a faulty statement, improve MUSE/MUSEUM results.  We reject such mutants in part to keep costs low, and in part because we think that the causal information contained in such mutants, that repair a failure but also break some passing test, is problematic.  They seem likely to be less useful as explanations of the causes of a failure, since they do not impact the program semantics in a way that is only known to be beneficial, and could potentially even mislead a user if used as explanations.

Discussion with the MUSE/MUSEUM authors confirms  that adding information for passing tests, while costly, would likely improve the MUSE and MUSEUM results, given the weakness of our oracles, particularly for SpiderMonkey, and should be considered essential for ideal application of their approach.  Because the cost of recording the full mutant analysis matrix for all passing tests (rather than considering a mutant killed as soon as one test fails, as we do) is very high, and we would like to produce a comparison over a fixed computational cost, we give results for MUSE/MUSEUM over failing tests only, cautioning that we are not sure what the impact of this choice is.  For similar reasons of keeping costs low, we also used the mutation operators of Andrews vs. the more extensive Proteum \cite{Proteum} operators used in MUSE/MUSEUM's evaluations.  Even with these restrictions, running all mutants on passing tests took about 3 times as long as the search for repairs, which we already consider a potentially problematic cost.

@@

\begin{comment}
\begin{figure}
{\scriptsize
\begin{code}
{\bf Diff of old ($<$) vs new ($>$) for 115 patch (portion):}
...
<             vp[1] = OBJECT\_TO\_JSVAL(thisp);
<         \} else \{
<             ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);
<         \}
...
<                   a->avail = (jsuword)sp;
<               \}
...
---
>         RESTORE\_SP(fp);
...
{\bf Mutant information:}
Failure repaired by 148 mutants.
...
\#3: delete statement mutant of jsinterp.c:944:

            vp[1] = OBJECT\_TO\_JSVAL(thisp);
        \} else \{
/*MUTANT    ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);*/
        \}

{\bf Coverage change information:}
...
\#6: 5 mutants (3.38\% of repairs) added jsinterp.c:992:
                   a->avail = (jsuword)sp; /* ADDED */
\end{code}
}
\caption{Patch and explanation for fault 115}
%\vspace{-0.18in}
\label{fig:explain}
\end{figure}
\end{comment}

@@

\begin{comment}
\subsubsection{Error Explanation}

Figure \ref{fig:explain} shows part of the patch for SpiderMonkey fault 115, and the {\bf Coverage} and {\bf Repair} outputs that successfully localize the fault (the 6th coverage change output, and the 3rd mutant output), to give some idea of the information our methods present.  For {\bf Coverage}, it is surprising that the sixth highest ranked change only appeared in 5 of 148 repairs. This change ranked high out of thousands of changes because it was unusual, appearing for only 10 repairs in the entire SpiderMonkey analysis.

The precise form an explanation based on our techniques should take is not clear.  One possibility, suggested by the results here, is a method focused on repairs, but using common coverage changes.  For each repairing mutant, in rank order, the highest ranking coverage changes for that mutant could also be shown, to give an idea of unusual (and potentially localizing) changes induced by repair.
\end{comment}

@@

For GCC wrong code faults, the baseline chance two test cases shared an underlying fault was 38.97\%.  Knowing that two test cases shared a repairing mutant raised the chance to 68.5\%, and knowing they disagreed on a fault lowered it to only 19.01\%.  The respective increase and decrease in probability of matching fault compared to baseline was thus 1.75 times greater for matching repairs, and less than 0.5 the chance of being the same fault, given one mismatched repair.  Knowing two test cases were both not fixed by a mutant again provided marginal evidence of sharing a fault: 39.2\% chance of matching faults.
For 99.3\% (all but 8) of the 1,090 non-singleton fault failures in GCC wrong code, the closest test case(s) by the repair metric matched fault.  The best previous reported FPF metric, function coverage vectors, had a matching rate of 92.2\%.   The mean and median numbers of repaired tests per mutant (for mutants that repaired any tests at all) were 18.4 and 3.0, respectively.  A few mutants fixed a very large number of tests, up to 1,050.  These all appear to be turning off all optimizations --- essentially running gcc in -O0 mode.  Most mutants fixed only a few tests, to a greater extent than was true with SpiderMonkey.    Mean homogeneity (\% of repaired tests corresponding to most common repaired fault) was 79.4\%, median 100\%.

@@

Mutation analysis is not cheap.  The experiments in this paper were run over a long period of time.  However, there are numerous ways to reduce costs.  First, the primary cost is compiling the mutated versions of the SUT.  Running each test case under each mutated version of the compiler is cheap: each execution requires around 0.05 seconds for SpiderMonkey, and 0.12 seconds for GCC, on average; moreover, executions can be done in parallel, most failures do not cover most mutants, and vice versa, so the total number of repair checks needed is far less than the product of mutants and failures, and can be spread over many machines.  The practical approach to fuzzer taming for a large, ongoing project is likely to maintain a set of ``hot'' pre-compiled mutants.  These can be pruned at will by running them on passing test cases, and removing mutants that fail on any test case.  
\begin{comment}
Keeping hot mutants for a heavily modified program could be costly (since each mutant must be recompiled, if not re-tested, for each modification to the code), but for stable releases this is a simple approach to keep costs low.
\end{comment}

>>>>

Table \ref{jstable} shows a comparison of three fault localization methods for the SpiderMonkey faults.  The first column shows, for each fault, identified by the commit number of the code change that first ``fixed'' the failing tests associated with the fault, its FPF ranking: this is \emph{not} a fault localization ranking, just a way to see that the localization success seems to be somewhat independent of the ease of distinguishing the failures for a fault.  The next four columns show localization rankings.  A dash for a column means that localization did not rank any faulty statements, or assigned all faulty statements suspiciousness of 0.0.  The four rankings are: the {\bf Coverage} localization, the {\bf Repair} localization, the MUSE \cite{MUSE} localization, and the MUSEUM \cite{multilingual} localization, which uses the same formula as MUSE, but works better for multiple faults because it uses only one failure.  The MUSE/MUSEUM formulas normally make use of information from passing tests as well: when mutating a statement makes a passing test case fail, it makes the statement \emph{less} suspicious, by a weighted amount. The weight assigned to information from passing tests in our setting would likely be low (due to the ratios of repairs to mutation kills).  In a limited sense, information from passing tests is already incorporated in our results.  Throwing out all mutants that are killed by any passing test as potential repairs/localizations ensures that the rankings of all statements that are in MUSE/MUSEUM rankings are correct, \emph{relative to each other}.  By definition, passing tests have no influence on the suspiciousness of these mutants.  However, there may be other mutants that 1) repair a failure and 2) are killed by some test case: these could, if enough different ones repaired the same faulty statement, improve MUSE/MUSEUM results, though in practice this is extremely unlikely.  We reject such mutants in part to keep costs low, and in part because we think that the causal information contained in such mutants, that repair a failure but also break some passing test, is problematic.  They seem likely to be less useful as explanations of the causes of a failure, since they do not impact the program semantics in a way that is only known to be beneficial, and could potentially even mislead a user if used as explanations.  Still, it is most useful to compare MUSEUM/MUSE and our approach on the cases where all methods produce a localization.

Discussion with the MUSE/MUSEUM authors confirms  that adding information for passing tests, while costly, would likely improve the MUSE and MUSEUM results, given the weakness of our oracles, particularly for SpiderMonkey, and should be considered essential for ideal application of their approach.  Because the cost of recording the full mutant analysis matrix for all passing tests (rather than considering a mutant killed as soon as one test fails, as we do) is very high, and we would like to produce a comparison over a fixed computational cost, we give results for MUSE/MUSEUM over failing tests only, cautioning that we are not sure what the impact of this choice is on faults that were not localized.  For similar reasons of keeping costs low, we also used the mutation operators of Andrews vs. the more extensive Proteum \cite{Proteum} operators used in MUSE/MUSEUM's evaluations.  Even with these restrictions, running all mutants on passing tests took about 3 times as long as the search for repairs, which we already consider a potentially problematic cost.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{comment}                                               %
% \begin{figure}                                                %
% {\scriptsize                                                  %
% \begin{code}                                                  %
% {\bf Diff of old ($<$) vs new ($>$) for 115 patch (portion):} %
% ...                                                           %
% <             vp[1] = OBJECT\_TO\_JSVAL(thisp);               %
% <         \} else \{                                          %
% <             ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);    %
% <         \}                                                  %
% ...                                                           %
% <                   a->avail = (jsuword)sp;                   %
% <               \}                                            %
% ...                                                           %
% ---                                                           %
% >         RESTORE\_SP(fp);                                    %
% ...                                                           %
% {\bf Mutant information:}                                     %
% Failure repaired by 148 mutants.                              %
% ...                                                           %
% \#3: delete statement mutant of jsinterp.c:944:               %
%                                                               %
%             vp[1] = OBJECT\_TO\_JSVAL(thisp);                 %
%         \} else \{                                            %
% /*MUTANT    ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);*/    %
%         \}                                                    %
%                                                               %
% {\bf Coverage change information:}                            %
% ...                                                           %
% \#6: 5 mutants (3.38\% of repairs) added jsinterp.c:992:      %
%                    a->avail = (jsuword)sp; /* ADDED */        %
% \end{code}                                                    %
% }                                                             %
% \caption{Patch and explanation for fault 115}                 %
% %\vspace{-0.18in}                                             %
% \label{fig:explain}                                           %
% \end{figure}                                                  %
% \end{comment}                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{comment}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        %
% \subsubsection{Error Explanation}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      %
%                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        %
%                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        %
% Figure \ref{fig:explain} shows part of the patch for SpiderMonkey fault 115, and the {\bf Coverage} and {\bf Repair} outputs that successfully localize the fault (the 6th coverage change output, and the 3rd mutant output), to give some idea of the information our methods present.  For {\bf Coverage}, it is surprising that the sixth highest ranked change only appeared in 5 of 148 repairs. This change ranked high out of thousands of changes because it was unusual, appearing for only 10 repairs in the entire SpiderMonkey analysis.  %
%                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        %
% The precise form an explanation based on our techniques should take is not clear.  One possibility, suggested by the results here, is a method focused on repairs, but using common coverage changes.  For each repairing mutant, in rank order, the highest ranking coverage changes for that mutant could also be shown, to give an idea of unusual (and potentially localizing) changes induced by repair.                                                                                                                                          %
% \end{comment}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

For GCC wrong code faults, the baseline chance two test cases shared an underlying fault was 38.97\%.  Knowing that two test cases shared a repairing mutant raised the chance to 68.5\%, and knowing they disagreed on a repair lowered it to only 19.01\%.  The respective increase and decrease in probability of matching fault compared to baseline was thus 1.75 times greater for matching repairs, and less than 0.5 the chance of being the same fault, given one mismatched repair.  Knowing two test cases were both not fixed by a mutant again provided marginal evidence of sharing a fault: 39.2\% chance of matching faults.
For 99.3\% (all but 8) of the 1,090 non-singleton fault failures in GCC wrong code, the closest test case(s) by the repair metric matched fault.  The best previous reported FPF metric, function coverage vectors, had a matching rate of 92.2\%.   The mean and median numbers of repaired tests per mutant (for mutants that repaired any tests at all) were 18.4 and 3.0, respectively.  A few mutants fixed a very large number of tests, up to 1,050.  These all appear to be turning off all optimizations --- essentially running gcc in -O0 mode.  Most mutants fixed only a few tests, to a greater extent than was true with SpiderMonkey.    Mean homogeneity (\% of repaired tests corresponding to most common repaired fault) was 79.4\%, median 100\%.

@@

Mutation analysis is not cheap.  The experiments in this paper were run over a long period of time.  However, there are numerous ways to reduce costs.  First, the primary cost is compiling the mutated versions of the SUT.  Running each test case under each mutated version of the compiler is cheap: each execution requires around 0.05 seconds for SpiderMonkey, and 0.12 seconds for GCC, on average; moreover, executions can be done in parallel, most failures do not cover most mutants, and vice versa, so the total number of repair checks needed is far less than the product of mutants and failures, and can be spread over many machines.  The practical approach to fuzzer taming for a large, ongoing project is likely to maintain a set of ``hot'' pre-compiled mutants.  These can be pruned at will by running them on passing test cases, and removing mutants that fail on any test case.

### 2017-04-30 introduction.tex
small fixes
IEEE format

The key insight of this paper is a hypothesis with numerous possible applications, including a universal fuzzer taming metric that can also provide assistance in debugging.

@@

The core idea is hardly controversial:  most developers determine if they have fixed all faults in a set of failing test cases by re-running the tests after they fix at least one fault.  As a method for fuzzer taming or debugging assistance, however, this is useless.  Fortunately, developer-provided patches are not the only source of syntactic changes to a program.  Mutation analysis \cite{demillo1978hints,budd1980theoretical} applies large numbers of syntactic changes to a program, usually to evaluate a test suite \cite{mutant,justmutants}.  Some recent work has also considered these changes as a source of fixes or localizations for program faults \cite{achour,multilingual,MUSE,DebroyMutant}.  Our experience, as well as empirical data \cite{GopinathMutants}, suggests that very few compiler faults are due to the kind of simple syntactic changes found in mutants.  However, this does not matter for {\bf Hypothesis 1};  what matters is that failures, which correspond to faults, can be made to succeed.  When a test case $t$ fails for program $P$ but succeeds for mutant $m$ of $P$ we say that $m$ \emph{repairs} $t$.  In most cases this does not mean that $m$ is the inverse of a fault, but that $m$ somehow avoids the consequence of a fault.  It is not important that repairs actually fix anything, if all we seek is a way to decide whether failures are due to the same fault.

@@

These hypothesis do not claim that being repaired by the same mutant perfectly predicts fault equivalence.  To understand why that seems highly unlikely, consider why a mutant of a compiler might cause a test case to stop failing.  Many, likely most, compiler faults are due to incorrect optimizations.  Turning an optimization off can cause a program to compile correctly.  Optimizations are generally guarded by conditional switches --- in some cases, so that the optimization can be turned off by a user, in other cases when a property of the code in question prevents the optimization.  If two failures become successes due to turning off an optimization, it is certainly some level of evidence they are the same fault, compared to the baseline probability.  Intuitively, the evidence provided seems much stronger than the fact that, e.g., the two test cases execute a shared line of code \cite{RepsSpectra}.  However, optimization guards range from guarding very specific fragments of code to guarding entire modules with many functions and related sub-optimizations.  If a mutant prevents a very specific optimization (consisting of a few lines of code) from executing, and repairs two tests, that is powerful evidence they are related.  If a mutant turns off a large number of optimizations, it is weak evidence.  Must we then characterize mutant granularity?  No.

@@

@@

The contributions of this paper are: hypotheses about how to measure distance between program executions, and practical proposals for using such a metric in fuzzer taming and in novel fault localization and explanation methods.  Evaluating the effectiveness of these methods also provides experimental evidence as to the validity of our hypotheses.  Our experimental results show that, for two realistic complex compilers, Mozilla's SpiderMonkey 1.6 JIT for JavaScript and GCC 4.3.0, using mutant response metrics improves FPF-based fuzzer taming over previous results \cite{PLDI13}, in multiple ways.  Our preliminary localization approaches compare favorably to state-of-the-art fault localization techniques \cite{MUSE,multilingual}, for the mutation analysis budget in our experiments.

>>>>

The key insight of this paper is based on an idea with numerous possible applications, including a universal compiler fuzzer taming metric that can also provide assistance in debugging.

@@

The core idea is hardly controversial:  most developers determine if they have fixed all faults in a set of failing test cases by re-running the tests after they fix at least one fault.  As a method for fuzzer taming or debugging assistance, however, this is useless.  Fortunately, developer-provided patches are not the only source of syntactic changes to a program.  Mutation analysis \cite{demillo1978hints,budd1980theoretical} applies large numbers of syntactic changes to a program, usually to evaluate a test suite \cite{mutant,justmutants}.  Some recent work has also considered these changes as a source of fixes or localizations for program faults \cite{achour,multilingual,MUSE,DebroyMutant}.  Our experience, as well as empirical data \cite{GopinathMutants}, suggests that very few compiler faults are due to the kind of simple syntactic changes found in mutants.  However, this does not weaken the value of the hypothesis; what matters is that failures, which correspond to faults, can be made to succeed.  When a test case $t$ fails for program $P$ but succeeds for mutant $m$ of $P$ we say that $m$ \emph{repairs} $t$.  In most cases this does not mean that $m$ is the inverse of a fault, but that $m$ somehow avoids the consequence of a fault.  It is not important that repairs actually fix anything, if all we seek is a way to decide whether failures are due to the same fault.

@@

These hypotheses do not claim that being repaired by the same mutant perfectly predicts fault equivalence.  To understand why that seems highly unlikely, consider why a mutant of a compiler might cause a test case to stop failing.  Many, likely most, compiler faults are due to incorrect optimizations.  Turning an optimization off can cause a program to compile correctly.  Optimizations are generally guarded by conditional switches --- in some cases, so that the optimization can be turned off by a user, in other cases when a property of the code in question prevents the optimization.  If two failures become successes due to turning off an optimization, it is certainly some level of evidence they are the same fault, compared to the baseline probability.  Intuitively, the evidence provided seems much stronger than the fact that, e.g., the two test cases execute a shared line of code \cite{RepsSpectra}.  However, optimization guards range from guarding very specific fragments of code to guarding entire modules with many functions and related sub-optimizations.  If a mutant prevents a very specific optimization (consisting of a few lines of code) from executing, and repairs two tests, that is powerful evidence they are related.  If a mutant turns off a large number of optimizations, it is weak evidence.  Must we then characterize mutant granularity?  No.

@@

Because of the difficulty in evaluating Hypotheses 1, 2, and 1a over general programs, in this paper we restrict our attention to the problem of assisting developers using automated compiler testing tools to debug production compilers.  We therefore evaluate a more modest proposal:  using distance metrics based on the causal approach suggested by these hypotheses, we can improve, in a statistically significant way, the ability to distinguish tests based on which underlying compiler faults they trigger.  Furthermore, fault localization based on the same metrics can successfully pinpoint the location of some compiler faults sufficiently to be likely to substantially aid debugging.

@@

The contributions of this paper include our hypotheses about how to measure distance between program executions, but most importantly are practical proposals for using such a metric in compiler fuzzer taming and fault localization and explanation.  Our experimental results show that, for two realistic complex compilers, Mozilla's SpiderMonkey 1.6 JIT for JavaScript and GCC 4.3.0, using mutant response metrics improves FPF-based fuzzer taming over best previous results \cite{PLDI13}, in multiple ways.  Our best preliminary localization approach also compare favorably to state-of-the-art fault localization techniques \cite{MUSE,multilingual}, for the mutation analysis budget in our experiments.
